\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-01 gwnnDraft02.tex
Added scenario details.

@@

@@

This is not the case if we consider the more generalized reheating scenarios of Sec.~\ref{sec:constraints}. Once the restriction that small vevs are preferentially reheated has been lifted, we can explore a landscape of standard sectors with much heavier particles (specifically quarks) and, as shown in section~\ref{sec:dQCD}, the SFOPT these entail. The key phenomenological constraint on such sectors is $\Delta N_{eff}$, giving us a maximum allowed temperature ratio (when compared to the SM) for each reheated hidden sector: Eq.~(\ref{eqn:energyDensityAllowed}) shows the maximum temperature ratios for specific numbers of additional hidden sectors. There are four scenarios that we examine here:

@@

\item \textbf{Maximized signal:} A single additional heavy hidden sector which saturates all current experimental bounds. In the $N$naturalness framework this is equivalent to reheating a standard sector with $i\sim 10^{16}$ up to the maximum allowed temperature ratio.
\item \textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have higgs vevs that are split by a factor of $\sqrt{10^3}$, leading to a large difference in the frequency of their gravitational wave signals.  In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{15}$ up to the maximum allowed temperature ratio.
\item \textbf{Medium split scenario:} Similar to the previous case: these sectors have higgs vevs that are split by a factor of $\sqrt{10}$, resulting in a much smaller difference in the frequency of their gravitational wave signals.  In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{13}$ up to the maximum allowed temperature ratio.
\item \textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are $\sim \sqrt{3}$ larger than the previous sector.

>>>>

\begin{equation}\label{eqn:alpha2}

@@

\begin{equation}\label{eqn:peakFrequency}

@@

This is not the case if we consider the more generalized reheating scenarios of Sec.~\ref{sec:constraints}. Once the restriction that sectors with small higgs' masses are preferentially reheated has been lifted, we can explore a much more vast landscape of hidden sectors than are allowed in the vanilla case. Here, we construct several different scenarios that are both detectable and demonstrate a variety of gravitational wave profiles. Specifically, we explore scenarios that lead to a deviation in the peak behaviour of the total GW signal (the convolution of stochastic GW from individual SFOPT) from a standard power law signal.

It should be noted that the key phenomenological constraint on all of these models is $\Delta N_{eff}$, giving us a maximum allowed temperature ratio (when compared to the SM) for each reheated hidden sector: Eq.~(\ref{eqn:energyDensityAllowed}) shows the maximum temperature ratios for specific numbers of additional hidden sectors. Due to the rather harsh scaling of the GW strength, $\alpha$, with temperature ratio (Eq.~(\ref{eqn:alpha2})), we take the optimistic approach of keeping the temperature ratio as high as possible for all of the hidden sectors.

In all our examined cases, we focus on heavy standard sectors --- pure Yang-Mills sectors with much heavier particles (specifically quarks) and, as shown in Sec.~\ref{sec:dQCD}, the SFOPT these entail. The reason for this arises from Eq.~(\ref{eqn:peakFrequency}): every exotic sector features a phase transition that occurs at $\Lambda_{ex} \sim 90$ MeV. If we maximize the allowed temperature ratio, this gives us a (SM) photon temperature, $T_{\gamma}$, that places our signal directly into the void between the detection region of pulsar timing arrays and space-based interferometers (see Sec.~\ref{sec:detection}). The location of the peak can be changed by dropping the temperature ratio, but the adjustment required to end up with a signal with an appropriate peak frequency makes the overall signal too weak to detect. In accordance with Sec.~\ref{sec:dQCD}, standard sectors can have much higher temperature phase transitions. As such, maintaining the maximum allowed temperature ratio between the hidden sector(s) and the SM gives a much larger photon temperature and a proportionally larger peak frequency; ultimately allowing for detection by space-based interferometers.

There are four scenarios that we examine here:

@@

\item \textbf{Maximized signal:} A single additional heavy hidden sector which saturates all current experimental bounds. The SM photon bath temperature at the time of the hidden sector PT is $87$ GeV. In the $N$naturalness framework this is equivalent to reheating a standard sector with $i\sim 10^{16}$ up to the maximum allowed temperature ratio.
\item \textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have higgs vevs that are split by a factor of $\sqrt{10^3} = (v_{h1})/(v_{h2})$. This results in a difference in the scale of the SFOPTs leading to the SM photon bath temperature changing a large amount during the time between the PTs. This, in turn, leads to a large separation in the peak frequency of their gravitational wave signals.  In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{15}$ up to the maximum allowed temperature ratio.
\item \textbf{Medium split scenario:} Similar to the previous case: these sectors have higgs vevs that are split by a factor of $\sqrt{10}= (v_{h1})/(v_{h2})$, resulting in a much smaller difference in the peak frequency of their gravitational wave signals. In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{13}$ up to the maximum allowed temperature ratio.
\item \textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are $\sqrt{3} \sim (v_{hi})/(v_{h(i+1)})$ larger than the previous sector.
